Staged Abstract Interpreter

### 2018-01-16 paper/paper.tex
misc

Extension: can we do it with small-step semantics? or staging a transition system?

@@

Another perspective: programs are data for an abstract interpreter, so if we have $n$ programs, 
then maybe there can be $n$ stages. 
Probably we can analyze first $m$ programs, and generate a residual abstract interpreter
waiting for the rest $(n-m)$ programs.
The abstract interpreter itself might be a partial abstract interpreter.

@@

>>>>

@@

Another perspective: programs are data for an abstract interpreter, so if we have $n$ programs, 
then maybe there can be $n$ stages. 
Probably we can analyze first $m$ programs, and generate a residual abstract interpreter
waiting for the rest $(n-m)$ programs.
These $(n-m)$ programs might be (abstract) arguments for the first $n$ programs, and
the abstract interpreter itself might be a partial abstract interpreter.

@@

6. Discussion

Big-step vs small-step

Futamura projection for abstract interpreter. Is there a second or third Futamura projection for
abstract interpreter?
